Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-02-08 paper/main.tex
added abbreviations for the modified maximum cardinality matching algrithm (MMCM) and bridge recognition (BR)

To find a matching $Q \subset E$, the following modified maximum cardinality matching algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e. the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $Q$. Add the edge connecting these two vertices to $Q$, and proceed to the next vertex until all vertices have been assessed. The pair of vertices incident to each edge in $Q$ are referred to as being ``matched'', and are connected by a ``matching'' edge.

During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in E$. Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$. It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$. This algorithm is able to create a matching set $Q$ in at most $O(n \log n)$ time.

Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP. Otherwise, if $Q$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$. $G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a procedure that selects suitable edges in $E$ to replace specific edges in $Q$, such that the components of $G'$ are merged together.

For each edge $(v_i, v_j) \in Q$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$. The procedure initially sorts the edges in $Q$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values. Any edges that are a result of rematching are then removed from this list. Starting from the first edge, the procedure searches through the list to find an edge that meets the following conditions:
\begin{enumerate}
	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $E$.
	\item The current edge and the succeeding edge are members of different components on $G'$.
\end{enumerate}

If such an edge is found, the procedure adds this edge to a set $C_i$, and continues to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $C_i$. Once there are no more valid edges to add to $C_i$, the procedure resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$. The procedure ends when the penultimate edge in the list has been examined.

The sets $C_1, C_2, ..., C_k$ created during this process are then analysed. In the event that the procedure has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':

>>>>

To find a matching $Q \subset E$, the following modified maximum cardinality matching (MMCM) algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e. the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $Q$. Add the edge connecting these two vertices to $Q$, and proceed to the next vertex until all vertices have been assessed. The pair of vertices incident to each edge in $Q$ are referred to as being ``matched'', and are connected by a ``matching'' edge.

During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in E$. Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$. It is guaranteed that MMCM will produce a maximum cardinality matching $Q \subset E$, and is able to do so in at most $O(n \log n)$ time.

Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP. Otherwise, if $Q$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$. $G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $E$ to be used as bridges between the components of $G'$, and will replace certain edges in $Q$.

For each edge $(v_i, v_j) \in Q$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$. The procedure initially sorts the edges in $Q$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values. Any edges that are a result of rematching are then removed from this list. Starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
\begin{enumerate}
	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $E$.
	\item The current edge and the succeeding edge are members of different components on $G'$.
\end{enumerate}

If such an edge is found, the procedure adds this edge to a set $C_i$, and continues to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $C_i$. Once there are no more valid edges to add to $C_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$. The procedure ends when the penultimate edge in the list has been examined.

The sets $C_1, C_2, ..., C_k$ created during this process are then analysed. In the event that BR has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
